Summary Tables

### 2020-01-09 summary_tables.Rmd
Add prop by mode and distance

>>>>

## Distance by mode by distance category

```{r trip_dist_mode_figs = "asis"}

for (city in cities){

  df <- io[[city]]$trip_scen_sets %>% filter(scenario == 'Baseline' & trip_mode %in% c('walking', 'bicycle', 'car', 'motorcycle', 'bus')) %>% distinct(trip_id, .keep_all = T) %>% group_by(trip_mode, trip_distance_cat) %>% summarise(sum_dist = sum(trip_distance), n_vals = n()) %>% 
    group_by(trip_mode) %>% mutate(n_vals_1 = sum(n_vals)) %>% 
    mutate(prop = round(n_vals/n_vals_1 * 100, 1))
  print(kable(df, caption = paste("Distance by mode by for  ", city)))
}

# Figures

```{r trip_dist_mode_figs = "asis"}

for (city in cities){

  df <- io[[city]]$trip_scen_sets %>% filter(scenario == 'Baseline' & trip_mode %in% c('walking', 'bicycle', 'car', 'motorcycle', 'bus')) %>% distinct(trip_id, .keep_all = T) %>% group_by(trip_mode, trip_distance_cat) %>% summarise(sum_dist = sum(trip_distance), n_vals = n()) %>% 
    group_by(trip_mode) %>% mutate(n_vals_1 = sum(n_vals)) %>% 
    mutate(prop = round(n_vals/n_vals_1 * 100, 1))

  print(ggplot(data=df, aes(x=trip_distance_cat, y=prop)) +
          geom_bar(stat="identity", fill="steelblue")+
          facet_wrap(vars(trip_mode)) +
          geom_text(aes(label=prop), vjust = -0.3, size = 3.5)+
          theme_minimal() +
          theme(panel.spacing = unit(2, "lines")) +
          labs(title = paste(city, ' by dist by mode')))
}
